Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-08 chapters/lit_review_new.tex
fixed figure ref in lit review

The energy of the system before and after particle adsorption is different and can be characterized for a simple system with parameters shown in Figure \ref{fig:fig:pieranski_model},

>>>>

The energy of the system before and after particle adsorption is different and can be characterized for a simple system with parameters shown in Figure \ref{fig:pieranski_model},
